Supermartingales and Termination Analysis of Statistical PCF

### 2020-10-08 probabilisticProgrammingMartingales.tex
Minor fix

If $(X,P) \sim_c (Y,P)$ then the final skeletons in $X$ and $Y$ are equal, and $(X,Q) \sim_c (Y,Q)$, therefore $\sim_c$ can be considered to apply to reduction sequences even without positions, $X \sim_c Y$ iff $(X,\cdot) \sim_c (Y,\cdot)$.

@@

\begin{proof}
A reduction sequence is in call-by-value order if for every pair of reductions in the sequence at positions $\alpha$ and $\beta$, where the reduction at $\alpha$ happens first, either $\alpha \leq \beta$ or $\alpha$ and $\beta$ are disjoint, with $\alpha$ to the left of $\beta$ (i.e.~the first elements of the sequences $\alpha, \beta$ where they differ are $@_1$ and $@_2$, $\underline f_i$ and $\underline f_j$ for $i < j$, or $\textsf{if}_i$ and $\textsf{if}_j$ for $i < j$, in that order. Note that although the reductions that occur in $X_{cbv}$ are in call-by-value order, it may not be the actual call-by-value reduction sequence because some redexes may remain un-reduced even when other reductions that should happen afterwards occur. It is only required that the reductions that do occur occur in the correct order.
\lo{This paragraph (especially the last sentence) is ambiguous.
What does it mean to say that that a reductions that occur in a reduction sequences are \emph{in CBV order}?}
\iffalse
\lo{So this is permitted?
\[
(II)(I (I \bar I)) \to
(II)(I\bar I) \to
(II)\bar I 
\]
but not this: 
\(
(II)(I (I \bar I)) \to
(II)(I \bar I) \to
(II)\bar I 
\)?}
\fi

>>>>

If $(X,P) \sim_c (Y,P)$ then the final skeletons in $X$ and $Y$ are equal, and $(X,Q) \sim_c (Y,Q)$, therefore $\sim_c$ can be considered to apply to reduction sequences even without positions, $X \sim_c Y$ iff $(X,\cdot) \sim_c (Y,\cdot)$. The structure of $\sim_c$ can be seen more clearly by choosing a canonical example from each equivalence class. For this, the member of the class that's in call-by-value order is used. A reduction sequence is in call-by-value order if for every pair of reductions in the sequence at positions $\alpha$ and $\beta$, where the reduction at $\alpha$ happens first, either $\alpha \leq \beta$ or $\alpha$ and $\beta$ are disjoint, with $\alpha$ to the left of $\beta$ (i.e.~the first elements of the sequences $\alpha, \beta$ where they differ are $@_1$ and $@_2$, $\underline f_i$ and $\underline f_j$ for $i < j$, or $\textsf{if}_i$ and $\textsf{if}_j$ for $i < j$, in that order). Note that although the reductions that occur in the sequence are in call-by-value order, it may not be the actual call-by-value reduction sequence starting from that point because some redexes may remain un-reduced even when other reductions that should happen afterwards occur. It is only required that the reductions that do occur occur in the correct order.

@@

\begin{proof}

\lo{This paragraph (especially the last sentence) is ambiguous.
What does it mean to say that that a reductions that occur in a reduction sequences are \emph{in CBV order}?}
\iffalse
\lo{So this is permitted?
\[
(II)(I (I \bar I)) \to
(II)(I\bar I) \to
(II)\bar I 
\]
but not this: 
\(
(II)(I (I \bar I)) \to
(II)(I \bar I) \to
(II)\bar I 
\)?}
\fi
